---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
library(lubridate)
df <- read.csv("activity.csv")  # read the data
df$date <- ymd(df$date)         # convert the date from string 'Factor' to date class

cc <- complete.cases(df)        # remove NA's
goodDf <- df[cc,]

```

## What is mean total number of steps taken per day?

```{r}
aggMean <- aggregate(steps ~ date, goodDf, mean)  # aggregate by date, take mean of number of steps
aggMedian <- aggregate(steps ~ date, goodDf, median)  # aggregate by date, take median of number of steps
aggSum  <- aggregate(steps ~ date, goodDf, sum)   # aggregate by date, take sum of number of steps

hist(aggSum$steps, breaks=20, xlab="steps per day", main="Number of steps per day")

extra <- data.frame(aggSum$date, aggSum$steps, aggMean$steps, aggMedian$steps)  # assemble new data frame to report mean, sum, median
names(extra) <- c("Date", "Sum", "Mean", "Median")
extra
```

## What is the average daily activity pattern?

```{r}
aggInterval <- aggregate(steps ~ interval, goodDf, mean)
plot(aggInterval$interval, aggInterval$steps, type = "l", xlab="Interval (each day)", ylab="Average number of steps")
title(main="Average number of steps per interval each day")

sorted <- aggInterval[with(aggInterval, order(steps, decreasing=TRUE)),]
maxInterval <- sorted[1,1]
maxAvgVal <- sorted[1,2]
```

The interval numbered `r maxInterval` is the one with the highest number of averages steps, `r maxAvgVal`.

## Imputing missing values

```{r}
sizeNA <- length(df[,1]) - length(which(cc))
```
The number of NA's in the original data set was `r sizeNA`.



## Are there differences in activity patterns between weekdays and weekends?
